---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
```{r pkg-knitr-opts, include=FALSE}
hrbrpkghelpr::global_opts()
```

```{r badges, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::stinking_badges()
```

```{r description, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::yank_title_and_description()
```

## Help Wanted/TODOs

### Issues

- [ ] Handle Licenses (PARTIAL SUPPORT EXISTS)
- [ ] Handle Authors (PARTIAL SUPPORT EXISTS)
- [ ] Get some buy-in on purls, BOM-refs, etc 
- [ ] Handle non-CRAN packages 
- [ ] Handle Shiny apps 
- [ ] Handle R "projects" 
- [ ] Dependency trees 
- [ ] Handle system requirements & (generically) stuff in src 

## What's Inside The Tin

The following functions are implemented:

```{r ingredients, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::describe_ingredients()
```

## Installation

```{r install-ex, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::install_block()
```

## Usage

```{r lib-ex}
library(sbom)

# current version
packageVersion("sbom")

```

```{r ex-01}
cat(x <- cran_pkg_sbom("ndjson"))
```

```{r ex-02}
validate_sbom(text=x)
```

## sbom Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a Contributor Code of Conduct. 
By participating in this project you agree to abide by its terms.
